### 2020-03-23 1_introduction.tex
Tweaks for spacing and wording.

How does one predict whether performance will be good enough for a given application?
The most commonly reported metrics,
\emph{weak} and \emph{strong} scaling, do not directly characterize
the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead by using sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from application costs
(such as increased communication) that scale with the number of nodes when
using progressively larger portions of a machine.

>>>>

How does one predict whether performance will be good enough for a given application?
The most commonly reported metrics,
\emph{weak} and \emph{strong} scaling, do not directly characterize
the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead by using sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from application costs
(such as communication) that scale with the number of nodes when
using progressively larger portions of a machine.

### 2020-03-23 3_implementation.tex
Tweaks for spacing and wording.

MPI~\cite{MPI} is a message-passing API for HPC. We provide an MPI
implementation written in the style of communicating sequential
processes (CSP). An excerpt of this implementation is shown in
Listing~\ref{lst:code-sample}.

@@

PGAS and actor models, such as Chapel~\cite{Chapel15},
Charm++~\cite{Charmpp93} and X10~\cite{X1005}, provide support for
asynchronous tasks that make them amenable to a straightforward
implementation of task bench. Synchronization is explicit and may be
provided by messages (in actor models) or other primitives, such as
locks or atomics (in PGAS models). PGAS models such as Chapel and X10
provide global references to data anywhere in the machine, but vary in
whether data can be accessed remotely or not (Chapel allows this, X10
does not).

Chapel also provides support for implicit parallelism which we do not
evaluate in this paper.

@@

Among the distributed task-based systems, one question is how to
resolve the inherent scalability bottleneck posed by enumerating tasks
sequentially. PaRSEC and StarPU resolve this by permitting the user to
omit tasks that are not directly connected in the dependence
graph. The program is replicated (for efficiency of the analysis), but
each task is executed only once. Because the dynamic checks to see if
a task should be executed are not free of cost, we also provide a
PaRSEC implementation (under the label \lstinline{shard}) which has
been hand-written to avoid all such checks. Regent performs an
equivalent optimization at compile time~\cite{ControlReplication17}
that does not require user intervention.

@@

Spark provides support for functional operators that implicitly map to
tasks. We use \lstinline[language=Scala]{flatMap} and
\lstinline[language=Scala]{groupByKey} to generate dependencies, and
then \lstinline[language=Scala]{mapPartitions} to execute a series of
tasks. An explicit hash partitioner ensures the correct task
granularity.

Swift/T~\cite{Wozniak13, Armstrong14} is a parallel scripting language
with dataflow semantics, used primarily for workflow automation. Our
implementation is straightforward.

>>>>

MPI~\cite{MPI} is a message-passing API for HPC. We provide an MPI
implementation written in the style of communicating sequential
processes (CSP). An excerpt is shown in Listing~\ref{lst:code-sample}.

@@

PGAS and actor models, such as Chapel~\cite{Chapel15},
Charm++~\cite{Charmpp93} and X10~\cite{X1005} offer
asynchronous tasks, making them amenable to a straightforward
implementation of task bench. Synchronization is explicit and may be
provided by messages (in actor models) or other primitives, such as
locks or atomics (in PGAS models). PGAS models such as Chapel and X10
provide global references to data anywhere in the machine, but vary in
whether data can be accessed remotely or not (Chapel allows this, X10
does not). Chapel also provides support for implicit parallelism which
we do not evaluate in this paper.

@@

Among distributed task-based systems, there can be a scalability
bottleneck due to enumerating tasks sequentially. PaRSEC and StarPU
resolve this by permitting the user to omit tasks that are not
directly connected in the dependence graph. The program is replicated
(for efficiency of the analysis), but each task is executed only
once. Because the dynamic checks to see if a task should be executed
are not free of cost, we also provide a PaRSEC implementation (under
the label \lstinline{shard}) which has been hand-written to avoid all
such checks. Regent performs an equivalent optimization at compile
time~\cite{ControlReplication17} that does not require user
intervention.

@@

Spark provides support for functional operators that implicitly map to
tasks. We use \lstinline[language=Scala]{flatMap} and
\lstinline[language=Scala]{groupByKey} to generate dependencies and
\lstinline[language=Scala]{mapPartitions} to execute tasks. An
explicit hash partitioner ensures the correct task granularity.

Swift/T~\cite{Wozniak13} is a parallel scripting language
with dataflow semantics, used primarily for workflow automation. Our
implementation is straightforward.

### 2020-03-23 5_evaluation.tex
Tweaks for spacing and wording.

To answer this question, we use the METG metric to determine the
smallest task granularity that can be executed at a given level of
efficiency as a proxy for overhead. Figure~\ref{fig:metg-compute}
shows how METG(50\%) varies with node count for a variety of
dependence patterns supported by Task Bench. METG(50\%) is calculated
separately at each node count, to distinguish runtime system behavior from
changes in communication latencies and topology when using
progressively larger portions of the machine.

@@

We observe that the baseline overheads of different
systems vary by over 5 orders of magnitude. It is worth
remembering when considering this metric that this is a \emph{minimum}
effective task granularity. Therefore applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical task granularities will
generally be determined by the application domain being
considered. Most notably, for large-scale data analytics workloads, the higher METG values observed for Spark and
TensorFlow are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.

@@

One advantage of systems with asynchronous execution capabilities is
the ability to mitigate load imbalance with little or no additional programmer effort, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency curves under load imbalance where each task's duration is multiplied by a uniform random variable between [0,~1). The task durations are generated with a deterministic
pseudo random number generator with a consistent seed to ensure
identical task durations for all systems.

>>>>

To answer this question, we use METG %% to determine the
%% smallest task granularity that can be executed at a given level of
%% efficiency
as a proxy for overhead. Figure~\ref{fig:metg-compute}
shows how METG(50\%) varies with node count for a variety of
dependence patterns supported by Task Bench. METG(50\%) is calculated
separately at each node count, to distinguish runtime system behavior from
changes in communication latencies and topology when using
progressively larger portions of the machine.

@@

We observe that the baseline overheads of different
systems vary by over 5 orders of magnitude. It is worth
remembering when considering this metric that this is a \emph{minimum}
effective task granularity. Applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical task granularities will
generally be determined by the application domain being
considered. Most notably, for large-scale data analytics workloads, the higher METG values observed for Spark and
TensorFlow are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.

@@

One advantage of asynchronous execution is
the ability to mitigate load imbalance with little or no additional programmer effort, especially in the presence of
task parallelism. To quantify this effect,
Figure~\ref{fig:efficiency-imbalance} plots task granularity vs
efficiency curves under load imbalance where each task's duration is multiplied by a uniform random variable between [0,~1). The task durations are generated with a deterministic
pseudo random number generator with a consistent seed to ensure
identical task durations for all systems.

### 2020-03-23 l2_mpi_sample.tex
Simplify code sample.
Tweaks for spacing and wording.

\begin{lstlisting}[language=C++,caption={Excerpt from Task Bench implementation in MPI.},label={lst:code-sample},style=codeblock,float]
void execute_task_graph(Graph g) {
  char *output = (char *)malloc(g.output_bytes);
  char *scratch = (char *)malloc(g.scratch_bytes);
  char **inputs = (char **)malloc(/*...*/);
  long rank;
  // initialize data structures...

@@

      g.execute_point(t, rank, output, g.output_bytes_per_task,
        inputs, input_bytes, idx,
        scratch, g.scratch_bytes_per_task);
    }
  }
}
\end{lstlisting}

>>>>

\begin{lstlisting}[language=C++,caption={Excerpt from Task Bench implementation in MPI.},label={lst:code-sample},style=codeblocktop,float]
void execute_task_graph(Graph g) {
  char *output = (char *)malloc(g.output_bytes);
  char *scratch = (char *)malloc(g.scratch_bytes);
  char **inputs = (char **)malloc(/*...*/);
  long rank;
  // initialize data structures...

@@

      g.execute_point(t, rank, output, inputs, scratch);
    }
  }
}
\end{lstlisting}
